Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
update ASS figs

\begin{itemize}
\item \emph{ob-closest}: the similarity between two scenes is equal to the largest similarity between their centroids.
\item \emph{ob-averaged}: the similarity between two scenes is equal to the average of their centroids similarities.
\item \emph{ob-weighted}: for each scene, each centroid is weighted according to the number of frames belonging to its cluster.
\end{itemize}

@@

For the \emph{ob} approaches (\emph{weighted}, \emph{closest} and \emph{average}), we use the precomputed kernels described in Section \ref{sec:object}. For both the \emph{ei} and \emph{li} approaches, a linear kernel as well as a RBF kernel are used. As for the \emph{ob} approaches, the RBF kernel is scaled locally using the method proposed in \cite{selfTuneManor2004}. All feature vectors, being frames, pooled frames or centroids, depending on the approach considered, are standardized prior to be filled into the classifier. The standardization is computed with respect to the train/test set splits of the cross validation scheme (see Section \ref{sec:stand}).

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{gfx/unsupervised_test1.eps}
\caption{... \ml{super, c'est propre}}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{gfx/unsupervised_test2.eps}
\caption{...}
\end{center}
\end{figure}

@@

\subsection{Object-based \vs early integration}

@@

\begin{table}
\begin{center}
\begin{tabular}{cccc}
                    & time-scattering & time-scattering & mfcc \\
                    & w/ log comp.    & w/o log comp.   &      \\
             \hline
early int. (linear)  & 66 (11)        & 62 (6)  & 46 (8)    \\
early int. (RBF)     & 60 (7)         & 57 (8)  & 60 (8)    \\
late int.  (linear)  & 75 (5)         & 70 (8)  & 63 (8)   \\
late int.  (RBF)     & 78 (6)         & 73 (8)  & 72 (10)   \\
ob-closest.          & 66 (7)         & 58 (6)  & 56 (9)   \\
ob-averaged.         & 61 (7)         & 54 (8)  & 61 (9)   \\
ob-weighted.         & 54 (11)        & 43 (10) & 51 (15)   \\
\end{tabular}
\caption{...}
\end{center}
\end{table}

>>>>

\begin{itemize}
\item \emph{ob-closest} (ob-c): the similarity between two scenes is equal to the largest similarity between their centroids.
\item \emph{ob-averaged} (ob-a): the similarity between two scenes is equal to the average of their centroids similarities.
\item \emph{ob-weighted} (ob-w): for each scene, each centroid is weighted according to the number of frames belonging to its cluster.
\end{itemize}

@@

For the \emph{ob} approaches, we use the precomputed kernels described in Section \ref{sec:object}. For both the \emph{ei} and \emph{li} approaches, a linear kernel as well as a RBF kernel are used. As for the \emph{ob} approaches, the RBF kernel is scaled locally using the method proposed in \cite{selfTuneManor2004}. All feature vectors, being frames, pooled frames or centroids, depending on the approach considered, are standardized prior to be filled into the classifier. The standardization is computed with respect to the train/test set splits of the cross validation scheme (see Section \ref{sec:stand}).

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{gfx/unsupervised_test1.eps}
\caption{ASS: $p@k$ obtained for the MFCC and the time-scattering with log compression}
\label{fig:ASS_1}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{gfx/unsupervised_test2.eps}
\caption{ASS: $p@k$ obtained for the time-scattering with and without log compression (w/o log)}
\label{fig:ASS_1}
\end{center}
\end{figure}

@@

What
\subsection{Object-based \vs early integration}

@@

\begin{table}
\begin{center}
\begin{tabular}{llll}
                    & time-scattering & time-scattering & mfcc \\
                    & w/ log comp.    & w/o log comp.   &      \\
             \hline
ei (linear)  & 66 (11)        & 62 (6)  & 46 (8)    \\
ei (RBF)     & 60 (7)         & 57 (8)  & 60 (8)    \\
li (linear)  & 75 (5)         & 70 (8)  & 63 (8)   \\
li (RBF)     & 78 (6)         & 73 (8)  & 72 (10)   \\
ob-c         & 66 (7)         & 58 (6)  & 56 (9)   \\
ob-a         & 61 (7)         & 54 (8)  & 61 (9)   \\
ob-w         & 54 (11)        & 43 (10) & 51 (15)   \\
\end{tabular}
\caption{...}
\end{center}
\end{table}
